Epilepsy example

### 2022-11-07 src/epil/epil.Rmd
Multiple random effects in one template now working -- (yeah buddy)

#' Prepare the initialisation parameters if it's nu that we're toggling
if(dat$toggle == 0) {
  param_fixed_theta[["nu_i"]] <- param_fixed_theta$nu[i]
  param_fixed_theta[["nu_minus_i"]] <- param_fixed_theta$nu[-i]
  # param_fixed_theta$nu <- NULL
}

#' Or if it's epsilon that we're toggling
if(dat$toggle == 1) {
  param_fixed_theta[["epsilon_i"]] <- param_fixed_theta$epsilon[i]
  param_fixed_theta[["epsilon_minus_i"]] <- param_fixed_theta$epsilon[-i]
  # param_fixed_theta$epsilon <- NULL
}

@@

# quad <- aghq::aghq(
#   ff = obj_fixed_theta,
#   k = 3,
#   startingvalue = 0,
#   control = aghq::default_control_tmb()
# )
#  
# pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = fine_grid)[[1]]
# 
# ggplot(pdf_and_cdf, aes(x = theta, y = pdf)) +
#   geom_line() +
#   theme_minimal() +
#   labs(x = "nu[1]", y = "Posterior")
```

>>>>

#' Prepare the initialisation parameters if it's nu that we're toggling
#' We fix the nu parameter to zero, as we're using nu_i and nu_minus_i
if(dat$toggle == 0) {
  param_fixed_theta[["nu_i"]] <- param_fixed_theta$nu[i]
  param_fixed_theta[["nu_minus_i"]] <- param_fixed_theta$nu[-i]
  map_fixed_theta[["nu"]] <- rep(factor(NA), length(param[["nu"]]))
}

#' Or if it's epsilon that we're toggling
#' We fix the epsilon parameter to zero, as we're using epsilon_i and epsilon_minus_i
if(dat$toggle == 1) {
  param_fixed_theta[["epsilon_i"]] <- param_fixed_theta$epsilon[i]
  param_fixed_theta[["epsilon_minus_i"]] <- param_fixed_theta$epsilon[-i]
  map_fixed_theta[["epsilon"]] <- rep(factor(NA), length(param[["epsilon"]]))
}

@@

ggplot(pdf_and_cdf, aes(x = theta, y = pdf)) +
  geom_line() +
  theme_minimal() +
  labs(x = "nu[1]", y = "Posterior")
```
